How to compute the fusion product of MV cycles in type A

### 2020-12-30 draft.tex

\begin{equation}
    \cW_\mu = G_1[t^{-1}]L_\mu
\end{equation}

@@

The family of semi-infinite orbits \acom{Maybe doesn't make sense before specialization?}
\begin{equation}
    S_{\mu_1,\mu_2} = N_-(\CC[t,t^{-1}, (t-s)^{-1}]) L_{\mu_1,\mu_2}\,. 
\end{equation}

The orbit of $\CC[t]$-lattices in $\CC(t)^m$ whose elements specialize again to $\CC\xt$-lattices in $\CC\xT^m$ away from $t = 0$ and away from $t = s$ as follows
\begin{equation}
    \label{eq:defGrBDlambda}
    \begin{split}
        (\Grbd[2])^{\lambda_1,\lambda_2} = \{L \in\Grbd[2] : 
        %L\otimes\CC[t^{-1}] 
        L_{\mu_1,\mu_2}\otimes \CC\xt[t-s] 
        &\in \Gr^{\lambda_2} \text{ and } \\
        % L\otimes\CC[(s-t)^{-1}] 
        L_{\mu_1,\mu_2}\otimes \CC\xt &\in \Gr^{\lambda_1}\}\,.
    \end{split}
\end{equation}
% 
\acom{These defining conditions are again just telling us that in the fibre over the fixed point $(0,s)\in C^{(2)}$ this set is pairs of lattices; note that we invert the indeterminates $t$ and $(t-s)$ \textit{after} specializing $(0,s)$. Could we give a more explicit characterization like $t^{N_1}(t-s)^{N_2} L_0 \subseteq L\subseteq t^{-N_1}(t-s)^{-N_2}$?}

@@

Let
$\cW_\mu = G_1[t^{-1}]t^\mu $ and $\hat \cW_\mu = G_1[[t^{-1}]] t^\mu$.

@@

\begin{corollary}
    The MVyBD isomorphism restricts to an isomorphism of subfamilies 
    \begin{equation}
        \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu_1,\mu_2}^+ \to \overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap S_{\mu_1,\mu_2}\,. 
    \end{equation}
\end{corollary}

\begin{proof}
    Let $ A \in \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu_1,\mu_2}^+$ and let $ g $ be the polynomial matrix formed by the Mirkovic-Vybornov isomorphism.  Then the diagonal entries of $ g $ are $ t^{\mu_{1,k}} (t-s)^{\mu_{2,k}}$ and we can factor
    $$ g = (g t^{-\mu_1}(t-s)^{-\mu_2}) t^{\mu_1}(t-s)^{\mu_2} \in N[t, t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$$
    So we get containment in one direction.
\end{proof}

@@

\begin{lemma}%[Roger's lemma]
    Let $\mu_1,\mu_2$ be dominant and let $s\in \AA^1 - \{0\}$. Then 
    \begin{equation}
        S_{\mu_1,\mu_2}^s \subset \hat \cW_\mu 
    \end{equation}
    where $\mu = \mu_1 + \mu_2$.
\end{lemma}

>>>>

We define
$$L_\mu = t^\mu, L_{\mu_1, \mu_2} = t^{\mu_1} (t-s)^{\mu_2} \in G((t^{-1}))/G[t]$$

\begin{equation}
    \cW_\mu = G_1[[t^{-1}]]L_\mu \subset G((t^{-1}))/G[t]
\end{equation}
a subscheme of the thick affine Grassmannian

@@

The family of semi-infinite orbits 
\begin{equation}
    S_{\mu_1,\mu_2} = N_-(\CC((t^{-1}))) L_{\mu_1,\mu_2}\,. 
\end{equation}

The orbit of $\CC[t]$-lattices in $\CC(t)^m$ whose elements specialize again to $\CC\xt$-lattices in $\CC\xT^m$ away from $t = 0$ and away from $t = s$ as follows
\begin{equation}
    \label{eq:defGrBDlambda}
    \begin{split}
        (\Grbd[2])^{\lambda_1,\lambda_2} = \{L \in\Grbd[2] : 
        %L\otimes\CC[t^{-1}] 
        L \otimes_{\CC[t]} \CC\xt[t-s] 
        &\in \Gr^{\lambda_2} \text{ and } \\
        % L\otimes\CC[(s-t)^{-1}] 
        L\otimes_{\CC[t]} \CC\xt &\in \Gr^{\lambda_1} \text{ and } \\ 
        L \otimes_{\C[t]} \CC\xt[t-a] = L_0 \text{ for all $ a \ne 0, s$} \}\,.
    \end{split}
\end{equation}

\jcom{It is important to add the condition that the lattices are trivial at $ a $.}
% 
\acom{These defining conditions are again just telling us that in the fibre over the fixed point $(0,s)\in C^{(2)}$ this set is pairs of lattices; note that we invert the indeterminates $t$ and $(t-s)$ \textit{after} specializing $(0,s)$. Could we give a more explicit characterization like $t^{N_1}(t-s)^{N_2} L_0 \subseteq L\subseteq t^{-N_1}(t-s)^{-N_2}$?}

@@

@@

\jcom{This is true as stated with the ``larger'' definition of $ \cW_\mu $.  In fact, for any $\lambda_1, \lambda_2$, it is true $ \overline{\Grbd[2]^{\lambda_2,\lambda_2}}\cap\cW_\mu $ is contained in a subset that we could call $ \cW_\mu^s$ which we could define as
$$
\cW_\mu^s = G_1[[t^{-1}]]t^\mu \cap G[t,t^{-1}, (t-s)^{-1}] / G[t]
$$
where we regard $G[t,t^{-1}, (t-s)^{-1}] / G[t] \subset G((t^{-1}))/G[t] $

The way to think about this is as follows: inside the thick affine Grassmannian we can consider the $G$-bundles trivialized away from just 0, $s$, or equivalently those lattices which become the standard lattice after tensoring with $ \CC[[t-a]] $ for any $ a \ne 0, s$.
}
\begin{corollary}
    The MVyBD isomorphism restricts to an isomorphism of subfamilies 
    \begin{equation}
        \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu_1,\mu_2}^+ \to \overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap S_{\mu_1,\mu_2}\,. 
    \end{equation}
\end{corollary}

\begin{proof}
    Let $ A \in \overline{\OO_{\lambda_1,\lambda_2}}\cap\TT_{\mu_1,\mu_2}^+$ and let $ g $ be the polynomial matrix formed by the Mirkovic-Vybornov isomorphism.  Then the diagonal entries of $ g $ are $ t^{\mu_{1,k}} (t-s)^{\mu_{2,k}}$ and we can factor
    $$ g = (g t^{-\mu_1}(t-s)^{-\mu_2}) t^{\mu_1}(t-s)^{\mu_2} \in N[t, t^{-1}, (t-s)^{-1}] t^{\mu_1} (t-s)^{\mu_2}$$
    So we get containment in one direction.

    For the reverse containment, we choose $ [g] \in G\overline{(\Grbd[2])^{\lambda_1,\lambda_2}}\cap S_{\mu_1,\mu_2}$.  By the lemma below, $[g] \in \cW_\mu$ and thus it lies in the image of our map and we are done.
\end{proof}

@@

\begin{lemma}%[Roger's lemma]
    Let $\mu_1,\mu_2$ be dominant and let $s\in \AA^1 - \{0\}$. Then 
    \begin{equation}
        S_{\mu_1,\mu_2}^s \subset \cW_\mu 
    \end{equation}
    where $\mu = \mu_1 + \mu_2$.
\end{lemma}
